Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Well, trying to get around this with a different package.

```{r eval=FALSE, echo=FALSE}
###################################
# Run the experiments with different sample sizes and tail thresholds

@@

>>>>

```
```{r eval=FALSE, echo=FALSE}
###################################
# Run the experiments with different sample sizes and tail thresholds

@@

# GP approach

Going off script here and going to try and do this in a way I understand it and with functions I already know.

```{r results='hide'}
library(extRemes)

fevd.mles <- data.frame(samp.size = rep(samp.sizes, length(thresh.vals)), threshold = thresh.vals, scale = 0, shape = 0, nllh = 0)

for(i in 1:nrow(fevd.mles)){
  ith.n        <- fevd.mles$samp.size[i]
  ith.samples  <- data.frame(x = sample(simplsamps$data, ith.n))
  # Can't use this because by setting those higher thresholds we have one data point and can't fit anything to it. 
  #ith.thresh   <- fevd.mles$threshold[i]

  # So, setting the threshold to 0 so we can compare to Lomax.
  ith.thresh <- 0

  ith.fit      <- fevd(ith.samples$x, threshold = ith.thresh, type = "GP")

  mles          <- summary(ith.fit)$par
  nll.hat       <- summary(ith.fit)$nllh
  BIC.mod       <- summary(ith.fit)$BIC

  fevd.mles$scale[i] <- mles[1]
  fevd.mles$shape[i] <- mles[2]
  fevd.mles$nllh[i]  <- nll.hat

```{r}
fevd.mles
```

So, we try to make the link to a Generalized Pareto distribution with the Lomax.The Lomax distribution is a special case of a Pareto where the parameters are as follows:  
- The location is $\mu = 0$ 
- The shape parameter is $\xi = 1/\alpha$
- The scale parameter is $\sigma = \lambda/\alpha$

Where the pdf of the lomax follows:
$$
p(x) = \frac{\alpha}{\lambda}\left[ 1 +  \frac{x}{\lambda}  \right]^{-\alpha + 1} = \left( \frac{\lambda}{x+\lambda} \right)^{\alpha} \left( \frac{\alpha}{x+\lambda} \right)
$$
And in JM Ponciano's parameterization: $\alpha = k$ and $\lambda = \alpha$, which means in comparison to the Generalized Pareto:

- The location is $\mu = 0$ 
- The shape parameter is $\xi = 1/k$
- The scale parameter is $\sigma = \alpha/k$

```{r}
gp2lomax.jmp <- function(shape, scale){
  k     <- 1/shape
  alpha <- scale*k
}
```

So, now we use the parameter estimates from the GP to get the parameters as a Lomax, and use those parameters to get the cdfs and means.

```{r}

fevd.mles %>% 
  mutate(ks = 1/shape,
         alphas = scale*ks) %>% 
  dplyr::select(-c(scale, shape)) %>% 
  mutate(est.cdf = lomax.cdf(threshold, alphas, ks),
         tail = 1- est.cdf, 
         mean = lomax.mean(alphas, ks)) -> est.lomax.mles
est.lomax.mles %>% knitr::kable()

And visually, we

```{r}
